---
title: "Glmnet"
author: "Oswaldo F. Domejean"
date: "March 14, 2016"
output: word_document
---

Libraries

```{r}
library(Metrics)
library(Matrix)
library(glmnet)
library(pROC)
library(caTools)
```

Data loading
```{r}
setwd("~/Documents/Data Mining/Kaggle/BNP Paribas Cardif Claims Management")
train <- read.table("trainV1.csv", header=T, sep=",")
test <- read.table("testV1.csv", header=T, sep=",") 

```

Model GLMNET: 

```{r}
#conjunto<-1:5000
#train=train[conjunto,]
#test=test[conjunto,]

train.label <- train[,(names(train) %in% c("target"))]
train.label <- as.factor(train.label)

train1=train[,!(names(train) %in% c("ID", "target"))]
test.label <- test[,(names(test) %in% c("ID"))]
test1=test[,!(names(test) %in% c("ID"))]

trainMatrix <- model.matrix(~., train1)
testMatrix <- model.matrix(~., test1)

BNPglmnetCV <- cv.glmnet(trainMatrix, train.label, family="binomial", nfolds=5)
  
#predGlmnetCV <- predict(BNPglmnetCV, testMatrix,type="response",
#                        s=BNPglmnetCV$lambda.min)

# test dataset prediction
#prediccion1 <- as.data.frame(cbind(test.label,predGlmnetCV))

#write.csv(prediccion1, "predGLMNETtest", row.names = FALSE)


###########################
#train.label <- train[,(names(train) %in% c("target"))]
#train.label <- as.factor(train.label)
#cv.train=train[,!(names(train) %in% c("ID", "target"))]
#test.label <- test[,(names(test) %in% c("ID"))]
#cv.test=test[,!(names(test) %in% c("ID"))]

k = 5
submission <- read.table("sample_submission.csv", header=TRUE, sep=',')
ensemble <- rep(0, nrow(test))
n = floor(nrow(train)/k)
for(i in 1:k){
  s1=((i-1)*n+1)
  s2=(i*n)
  subset=s1:s2
  train.label <- train[-subset,(names(train) %in% c("target"))]
  train.label <- as.factor(train.label)
  cv.train=train[-subset,!(names(train) %in% c("ID", "target"))]
  test.label <- train[subset,(names(test) %in% c("ID"))]
  cv.test=train[subset,!(names(test) %in% c("ID"))]

  trainMatrix <- model.matrix(~., cv.train)
  testMatrix <- model.matrix(~., cv.test)

  BNPglmnet <- glmnet(trainMatrix,
                      train.label,
                      family="binomial")

  testMatrix <- model.matrix(~., test[,!(names(test) %in% c("ID"))])
  predGlmnet <- predict(BNPglmnet, testMatrix,type="response",
                        s=BNPglmnetCV$lambda.min)
  ensemble <- ensemble + predGlmnet
}

# test dataset prediction

submission$PredictedProb <- ensemble/i
write.csv(submission, "predGLMNETtest", row.names = FALSE)
